method

### 2021-11-12 06_Paper/ER-ED/method.Rmd
changed file names and deleted non csv files

```{r import, echo=FALSE, message=FALSE, warning=FALSE}

```

>>>>

```{r import, echo=FALSE, message=FALSE, warning=FALSE}
# import ER ratings and ER discounting data into lists

datalist_ER = lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"), pattern = '*_ER.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)

datalist_ED = lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"), pattern = '*_ED.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)
```
